Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction

### 2019-11-24 docs/article.tex
Almost the end! We must now review the text!

@@

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction}
\author{Hiago Matheus Brajato \& André Furlan - UNESP - Universidade Estadual Paulista "Júlio de Mesquita Filho"}
\date{2019-11-14}
\maketitle

@@

\section{Image Acquisition}
\par The used dataset in this work is composed by 50 images of breast cells, being that 24 images are of malignant tumors and 26 of benign ones. Informations about this dataset can be found in \cite{artigo_database} and \href{https://bioimage.ucsb.edu/research/bio-segmentation}{\textbf{https://bioimage.ucsb.edu/research/bio-segmentation}}. The Figure \ref{fig:imagem3} below presents a flowchart of the sequence of steps developed in the application.

@@

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.7\linewidth]{images/fourrierFiltering/maskedImage}
		\caption{Image with mask}
		\label{fig:maskedimage}
	\end{figure}
\section{Segmentation}
\par The segmentation is an important step within the image processing, which is responsible for subdividing  an image in regions or objects that compose the signal \cite{Gonzalez:2006:DIP:1076432}, usually, this process is made through the separation of the image between background and object. Several techniques can be used in this process, such as based on thresholding, edge detection, region approaches. In this work, the optimal thresholding technique called Otsu was chosen due to its simplicity and good results. The segmentation was made after the filtering step, and the approach taken in the present work is to subtract the background of the segmented image from the original gray levels image. The code responsible for doing this task and the result produced in the image are shown in the Figure \ref{fig:imagem_segmentacao}.

@@

\section{Feature Selection}
The feature vector composed in the last step is formed by all descriptors presented in Figure \ref{fig:table_descriptors}, but it is not a good idea providing the feature vectors with all attributes as input to the classifiers, because the probability of the classification does not achieve good results is large doing the process in this way. This can be explained from the problem so-called "Curse of Dimensionality": after a certain number of descriptors, increasing the length of the feature vector with more attributes can degrade the performance of the classifiers.\par
In order to obtain the more relevant descriptors and the best number of attributes, the feature vector with 7175 descriptors was examined by the ReliefF method, which is responsible for ranking the importance of the predictors based on its capability of distinguishing samples of different classes. The next section presents the analysis made by the ReliefF, taking into consideration the performance of the classifiers.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=18.3cm]{images/results/finalResults.pdf}
    \caption{Average rates for AUC varying the number of descriptors taking into consideration the classifiers: Decision Tree, Discriminant Analysis and Naive Bayes}
    \label{fig:finalResults}
\end{figure}

\section{Results}
\par Like was shown in the previous section

\section{Conclusion}
lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

>>>>

\usepackage{color, colortbl}

@@

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
 T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}
	\title{Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction}
	\author{Hiago Matheus Brajato \& André Furlan - UNESP - Universidade Estadual Paulista "Júlio de Mesquita Filho"}
	\date{2019-11-14}
	\maketitle

@@

		\par The documents, code and images produced can be downloaded at \url{https://github.com/ensismoebius/Trabalho2-PDI}

	\section{Image Acquisition}
		\par The used dataset in this work is composed by 50 images of breast cells, being that 24 images are of malignant tumors and 26 of benign ones. Information about this dataset can be found in \cite{artigo_database} and \href{https://bioimage.ucsb.edu/research/bio-segmentation}{\textbf{https://bioimage.ucsb.edu/research/bio-segmentation}}. The Figure \ref{fig:imagem3} below presents a flowchart of the sequence of steps developed in the application.

@@

			\begin{figure}[h]
				\centering
				\includegraphics[width=0.7\linewidth]{images/fourrierFiltering/maskedImage}
				\caption{Image with mask}
				\label{fig:maskedimage}
			\end{figure}

	\section{Segmentation}
		\par The segmentation is an important step within the image processing, which is responsible for subdividing  an image in regions or objects that compose the signal \cite{Gonzalez:2006:DIP:1076432}, usually, this process is made through the separation of the image between background and object. Several techniques can be used in this process, such as based on thresholding, edge detection, region approaches. In this work, the optimal thresholding technique called Otsu was chosen due to its simplicity and good results. The segmentation was made after the filtering step, and the approach taken in the present work is to subtract the background of the segmented image from the original gray levels image. The code responsible for doing this task and the result produced in the image are shown in the Figure \ref{fig:imagem_segmentacao}.

@@

	\section{Feature Selection}
		The feature vector composed in the last step is formed by all descriptors presented in Figure \ref{fig:table_descriptors}, but it is not a good idea providing the feature vectors with all attributes as input to the classifiers, because the probability of the classification does not achieve good results is large doing the process in this way. This can be explained from the problem so-called "Curse of Dimensionality": after a certain number of descriptors, increasing the length of the feature vector with more attributes can degrade the performance of the classifiers.\par
		In order to obtain the more relevant descriptors and the best number of attributes, the feature vector with 7175 descriptors was examined by the ReliefF method, which is responsible for ranking the importance of the predictors based on its capability of distinguishing samples of different classes. The next section presents the analysis made by the Relief, taking into consideration the performance of the classifiers.

@@

	\section{Results}
		\par Like was shown in the previous section the number found to be the optimal in order to classify the data with the least error as possible is \textbf{six}.

		\par According to the graph shown in the figure \ref{fig:finalResults} right after the amount of five descriptors its possible to note a spike witch gives the best performance in terms of classification and, after this point, the classification results slowly decay and that, at least for this problem, the \textbf{decision tree} classifier had the best results.

		\par Individually, the table \ref{tab:topTenExperiment} shows the best results for each classifier, the dashed black vertical line indicates the \textit{locus} of best values. The confusion matrices \ref{fig:decisiontreeconfusion}, \ref{fig:discrimanalysisconfusion} and \ref{fig:naivebayesconfusion} shows the amount misclassified and correctly classified images, and finally, the ROCs curve are shown at \ref{fig:decisiontreeroc}, \ref{fig:discrimanalysisroc} and \ref{fig:naivebayesroc}.

		\begin{table}[ht]
			\centering
			\begin{tabular}{|c|c|c|c|c|}
				\hline 
				Descriptors & discrim\_analysis & decision\_tree & naive\_bayes & Average \\
				\hline 
				1 & 0,67 & 0,59 & 0,61 & 0,63 \\
				\hline 
				2 & 0,76 & 0,80 & 0,76 & 0,77 \\
				\hline 
				3 & 0,69 & 0,76 & 0,76 & 0,74 \\
				\hline 
				4 & 0,69 & 0,75 & 0,78 & 0,74 \\
				\hline 
				5 & 0,69 & 0,74 & 0,76 & 0,73 \\
				\hline 
				6 & 0,77 & \textbf{0,86} & \textbf{0,83} & \textbf{0,82} \\
				\hline 
				7 & 0,79 & 0,82 & \textbf{0,83} & 0,82 \\
				\hline 
				8 & \textbf{0,81} & 0,78 & 0,81 & 0,80 \\
				\hline 
				9 & \textbf{0,81} & 0,78 & 0,77 & 0,79 \\
				\hline 
				10 & 0,77 & 0,82 & 0,79 & 0,80\\
				\hline 
			\end{tabular} 
			\caption{First ten results of experiment (The best values highlighted)}
			\label{tab:topTenExperiment}
		\end{table}
		\begin{figure}[h]
			\centering
			\includegraphics[width=0.5\textwidth]{images/results/finalResults.pdf}
			\caption{Average rates for AUC varying the number of descriptors taking into consideration the classifiers: Decision Tree, Discriminant Analysis and Naive Bayes}
			\label{fig:finalResults}
		\end{figure}
		\begin{figure}[hb]
			\centering
			\includegraphics[width=0.7\linewidth]{images/results/decision_treeConfusion}
			\caption{Decision tree confusion matrix}
			\label{fig:decisiontreeconfusion}
		\end{figure}

		\begin{figure}[ht]
			\centering
			\includegraphics[width=0.7\linewidth]{images/results/discrim_analysisConfusion}
			\caption{Discriminate analysis confusion matrix}
			\label{fig:discrimanalysisconfusion}
		\end{figure}

		\begin{figure}[ht]
			\centering
			\includegraphics[width=0.7\linewidth]{images/results/naive_bayesConfusion}
			\caption{Naive Bayes confusion matrix}
			\label{fig:naivebayesconfusion}
		\end{figure}

		\begin{figure}[!htp]
			\centering
			\includegraphics[width=0.7\linewidth]{images/results/decision_treeROC}
			\caption{Decision tree ROC curve}
			\label{fig:decisiontreeroc}
		\end{figure}

		\begin{figure}[!htp]
			\centering
			\includegraphics[width=0.7\linewidth]{images/results/discrim_analysisROC}
			\caption{Discriminate analysis ROC curve}
			\label{fig:discrimanalysisroc}
		\end{figure}

		\begin{figure}[!htp]
			\centering
			\includegraphics[width=0.7\linewidth]{images/results/naive_bayesROC}
			\caption{Naive Bayes ROC curve}
			\label{fig:naivebayesroc}
		\end{figure}

	\section{Conclusion}
		\par The classification without the filtering and segmentation steps are noticeably worse, so these phases of the image processing are crucial for a good classification performance.
		\par It is important to note that find the right number of descriptors for each method of classification raises the accuracy of algorithms although it can be a heavy work for the computer.
